A Framework for Equivalence of Cast Calculi and a new Cast Representation

### 2020-10-05 paper.tex
removed old comment

Fig.~\ref{fig:R-machine-syntax} defines machine 
states $s$, including a definition of values $v$ and value typing.
Fig.~\ref{fig:R-machine-dynamics} defines the transition relation of the CEK
machine (\CMachine{B}).
We name the machine after \textbf{c}ast calculus.
%
% This machine is parameterized over blame strategy $B$, which ranges over
% Lazy D (Fig.~\ref{fig:blame-strategy-LazyD}) and Lazy UD 
% (Fig.~\ref{fig:blame-strategy-LazyUD}).
This machine is parameterized over blame strategy $B$. We will describe
the components of a blame strategy as we go through the machine definition.
In this work we focus on Lazy D (Fig.~\ref{fig:blame-strategy-LazyD}) and Lazy UD 
(Fig.~\ref{fig:blame-strategy-LazyUD}). Adding more blame strategies, 
such as the ones defined in \cite{siek2009exploring}, is possible.
\todo[inline]{JS: I don't think $B$ is restricted to just those two.
Can't it be any blame strategy that satisfies certain conditions?}
\todo[inline]{KC: Technically a $B$ should define a predicate over pretypes, which specifies
what is injectable, and a apply-cast function. Of course, the set of values that the apply-cast
function works with depends on the set of injectable types.
\url{https://github.com/Gradual-Typing/Equivalence-of-Cast-Calculi/blob/master/equivalence-of-cast-calculi/R/BlameStrategies.agda}
Do you want me to put these contraints in the paper?}
\todo[inline]{JS: Yes.}
\todo[inline]{KC: The machine definition gives a nice context for blame strategy so I 
define blame strategy later. You will find a todo near the blame strategy definition.}
%
The transitions involving casts are highlighted in red and described in
more detail below. The other transitions are standard for a CEK
machine for an extended simply typed lambda calculus~\citep{Felleisen:2009aa}.
%
Recall that CEK machines involve two kinds of transitions: those that
dive further into an expression (looking for a redex) and push an
entry onto the continuation and those that return a value to the
current continuation and possibly perform a computation.  That is, the
machine state is either in an evaluating $\sexpr{e}{E}{K}$ or
returning $\scont{v}{K}$ configuration, respectively. Additionally,
there are two halting configurations: \shalt{v} halts with a value,
while \error{l} halts with a blame label.  Observables include all the
value constructors and blame labels, as in the work of
\citet{siek2012interpretations}.  The function that converts values to
observables ($observe(v) = o$) is defined in the obvious way.

>>>>

Fig.~\ref{fig:R-machine-syntax} defines machine 
states $s$, including a definition of values $v$ and value typing.
Fig.~\ref{fig:R-machine-dynamics} defines the transition relation of the CEK
machine (\CMachine{B}).
We name the machine after \textbf{c}ast calculus.
%
% This machine is parameterized over blame strategy $B$, which ranges over
% Lazy D (Fig.~\ref{fig:blame-strategy-LazyD}) and Lazy UD 
% (Fig.~\ref{fig:blame-strategy-LazyUD}).
This machine is parameterized over blame strategy $B$. We will describe
the components of a blame strategy as we go through the machine definition.
In this work we focus on Lazy D (Fig.~\ref{fig:blame-strategy-LazyD}) and Lazy UD 
(Fig.~\ref{fig:blame-strategy-LazyUD}). Adding more blame strategies, 
such as the ones defined in \cite{siek2009exploring}, is possible.
%
The transitions involving casts are highlighted in red and described in
more detail below. The other transitions are standard for a CEK
machine for an extended simply typed lambda calculus~\citep{Felleisen:2009aa}.
%
Recall that CEK machines involve two kinds of transitions: those that
dive further into an expression (looking for a redex) and push an
entry onto the continuation and those that return a value to the
current continuation and possibly perform a computation.  That is, the
machine state is either in an evaluating $\sexpr{e}{E}{K}$ or
returning $\scont{v}{K}$ configuration, respectively. Additionally,
there are two halting configurations: \shalt{v} halts with a value,
while \error{l} halts with a blame label.  Observables include all the
value constructors and blame labels, as in the work of
\citet{siek2012interpretations}.  The function that converts values to
observables ($observe(v) = o$) is defined in the obvious way.
